---
title: 'Code Appendix: Multiple Regression Final Project extension'
author: "Ngoc Dinh, Zoe Meers, Monica Swartz"
date: "November 20, 2016"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r, include=FALSE}
#install.packages("mosaic")
#install.packages("dplyr")
#install.packages("stringr")
#install.packages("tidyr")
#install.packages("readr")
#install.packages("leaps")
#install.packages("car")
#install.packages("glmnet")
#install.packages("boot")
#install.packages("hash")
require(mosaic)
require(dplyr)
require(stringr)
require(tidyr)
require(readr)
require(leaps)
require(car)
require(glmnet)
require(boot)
```

#1. Data cleaning 
```{r, message=FALSE, warning=FALSE}
cses4 <- read_csv("C:/Users/stuadmin/Desktop/Projects/cses4_csv/cses4.csv")
```


This data has 448 variables and 51663 observations.
```{r}
dim(cses4)
```

Many variables are completely irrelevant to this research topic, which are removed from the dataset. 
```{r}
getUnusedVars <- function(col_name){
  variable_number = as.numeric(str_sub(col_name,2,5))
  return((variable_number<2001 & variable_number!=1004 & variable_number!=1006) |
      variable_number > 3017 |
      variable_number %in% c(3005,3006,3007,3008,3011,3012,3013,3015,3016,3021,3025))
}

remove=lapply(names(cses4),getUnusedVars)

political_data=cses4[-which(remove==TRUE)]

```

I also choose to include survey year (to calculate the age at the time of the survey) and country:
```{r}
political_data= political_data %>%
  mutate(Survey_Year=as.integer(str_sub(D1004,-4,-1)),
         Country=D1006_NAM,
         D1006_NAM=NULL, 
         D1004=NULL,
         D1006_UN=NULL,
         D1006=NULL)
```

#####Structure and name

```{r}
dim(political_data)
```

After removing irrelevant variable sections, there are now 54 variables that we will use to select the best model. 

```{r}
names(political_data)
```

The variable names are not clear and need to be renamed to something more descriptive.

From the codebook, I know that missing/privacy restricted values in this data are coded as 7-9, 95-99, 995-999, 9995-9999, 99995-99999 depending on the value range of the variable. These numbers are outside the range of the variable values; therefore, leaving these values unchanged can create high leverage points. I create a function to set coded NA values back to NA.

```{r}
setNA <- function(column){
  # Set coded NA values back to NAs
  #   Args: the dataset
  #   Returns: the new dataset, with coded NA values back as NAs.
    if (max(column)==9){
      column[which(column>6)] <- NA 
    } else if (max(column)==99){
      column[which(column>94)] <- NA 
    } else if (max(column)==999){
      column[which(column>994)] <- NA 
    } else if (max(column)==9999){
      column[which(column>9994)] <- NA 
    } else if (max(column)==99999){
      column[which(column>99994)] <- NA 
    }
  return(column)
}

political_data=lapply(political_data, setNA)

```


```{r}
str(political_data)
```

All variables are currently in numeric types, but most of them are actually categorical (factor). I create a function to change categorical variables to factor type and leave numeric variables unchanged. Of the remaining variables, only birth year and political spectrum (left/right wing) are numeric

```{r, results="hide"}
convertToFactor <- function(mydata){
  # Convert categorical variables to factor, leaving quantitative variables unchanged
  # Args: the dataset
  # Returns: the modified data
  data_with_factor <- mydata %>%
  mutate_each(funs(as.factor)) %>%
  mutate(D2001_Y=as.numeric(as.character(D2001_Y)),
         D3014=as.numeric(as.character(D3014)),
         D2021=as.numeric(as.character(D2021)))
  return(data_with_factor)
}
political_data=convertToFactor(as.data.frame(political_data))
str(political_data)

```

For convenience while doing the backward elimination algorithm, I move the dependent variable(Left/Right Wing, or D3014 in the codebook) to the first column and rename it to Left_Right_Wing
```{r}
data_x=political_data%>%
  mutate(D3014=NULL)
D3014=political_data$D3014
political_data=cbind(D3014, data_x)
political_data = political_data%>%
  rename("Left_Right_Wing"=D3014)
```


My preliminary variable check show that there are a lot of missing values in the data. If I remove all observations with at least one variable missing, there will be no data left to use. Hence I need to remove variables that have too many missing values, since values with are usually not useful.
The challenge here is that the more variable I include, the smaller the sample size gets, but if I include few variables, I risk removing useful variables. After some trial and error, I choose to remove variables that have more than 18000 missing values, which leaves me with 38 variables and 1308 observations 

```{r,results="hide"}
checkNumNALimit <- function(column, NA_limit){
  # Remove variables that have the number of missing values above a certain limit
  # Args:
  #   mydata: the dataset
  #   NA_limit: the maximum number of NA values allowed in a variable
  # Returns: the new dataset: missing values are removed and variables with the number of missing values
  # above the limit are removed
    return (sum(is.na(column))>NA_limit)
}

col_to_remove=lapply(political_data, function(x) checkNumNALimit(x,25000))
political_data=political_data[-which(col_to_remove==TRUE)]
str(political_data)
```

I rename the variables into more descriptive names
```{r}
political_data = political_data %>% 
  rename("Birth_Year"=D2001_Y, 
         "Gender"=D2002, 
         "Education"=D2003, 
         "Marital_Status"=D2004, 
         "Union_Membership"=D2005,
         "Union_Membership_Family"=D2006,
         "Farmer_Assosication"=D2008,
         "Employ_Status"=D2010,
         "Occupation"=D2011,
         "Public_Private_Employ"=D2013,
         "Employ_Status_Spouse"=D2015,
         "Household_Income"=D2020,
         "Number_Household"=D2021,
         "Num_Young_Child"=D2022,
         "Religious_Attendance"=D2024,
         "Religiousity"=D2025,
         "Religious_Denomination"=D2026,
         "Region"=D2028,
         "Rural_Urban"=D2031,
         "District"=D2032,
         "Birth_COuntry"=D2033,
         "Public_Expense_Health"=D3001_1,
         "Public_Expense_Edu"=D3001_2,
         "Public_Expense_UnEmpl"=D3001_3,
         "Public_Expense_Defense"=D3001_4,
         "Public_Expense_Pension"=D3001_5,
         "Public_Expense_Business"=D3001_6,
         "Public_Expense_Police"=D3001_7,
         "Public_Expense_Welfare"=D3001_8,
         "Improv_Standard"=D3002,
         "Economy"=D3003_1,
         "Gov_Action_Dif_Income"=D3004,
         "Power_Make_Dif"=D3009,
         "Vote_Make_Dif"=D3010,
         "Satisfaction_Democrat"=D3017) %>%
           mutate(Age=as.numeric(as.character(Survey_Year)) - as.numeric(as.character(Birth_Year)), Birth_Year=NULL, Survey_Year=NULL)
```

```{r}
final_political_data=na.omit(political_data)
dim(final_political_data)
```



#Model Selection

##1. Automatic Variable Selection:

###Step 1: Backward Elimination Algorithm

I run the algorithm the first time to remove completely irrelevant variables. I set the p-value cut-off to be 0.1, to eliminate the risk of removing relevant variables

```{r, result="hide"}
getIndexFromName <- function(mydata,name){
  # Return the index of a given variable in the dataset
  # Args: 
  #   mydata: the data set
  #   name: the name of the variable
  # Returns:
  #   The index of that variable
  result=which(names(mydata)==name)
  return (result)
}

backwardElim <- function(mydata, min_var, kfold){
  # Perform backward elimination to choose the best model
  # Args: 
  #   mydata: the dataset
  #   min_var: the minimum number of variables we want to include
  # Returns: the data with the minimum number of variables
  # Prints out the variables, R-squared, and AIC for each model.
  
  min_var_reached=FALSE
  data_model_selection=mydata
#while the number of variables are more than the minimum number of variables
  while(!min_var_reached){
    
    #perform regression on all the variables
    regression=lm(Left_Right_Wing ~., data=data_model_selection) 
    
    #get the table of overall significance (of each factor variables across all levels), variable name, and p-value of overall significance
    anova_model=anova(regression)
    var_name=row.names(anova_model)[-length(row.names(anova_model))]
    p_value=anova_model[1:length(anova_model[,1])-1,5]
  
    #create a table of variable name and their corresponding overall significance p-value
    p_value_table=data.frame(var_name, p_value)
  
    #find the least significant variable: its index, name, and p-value
    least_significant=which.max(p_value_table$p_value)
    least_significant_name=p_value_table$var_name[least_significant]
    max_p_value=p_value_table$p_value[least_significant]
    
    #if the number of variables is equal to the minimum, end loop
    if (length(p_value)==min_var){
      min_var_reached=TRUE
    } 
    
    #otherwise, set the p-value of the least significant variable to 0 in the p-value table
    p_value_table$p_value[least_significant]=0
    
    #Find the least significant variable in the data table by name, then remove it 
    index_removed=getIndexFromName(data_model_selection, least_significant_name)
    data_model_selection=data_model_selection[-index_removed]
    
    #If the least significant p-value is less than 0.05, meaning that all variables are signficant,
    #print out variable names, R-squared, and AIC for model selection
    if (max_p_value < 0.1){
      print("Variables:")
      print(var_name)
      print(paste("Adj R-squared:",summary(regression)$adj.r.squared,sep=" "))
      print(paste("AIC:",AIC(regression),sep=" "))
      if (kfold){
        set.seed(20)
        cv.error.10=rep(0 ,10)
        for (i in 1:10){
          glm.fit=glm(Left_Right_Wing ~. ,data=data_model_selection)
          cv.error.10[i]=cv.glm(data_model_selection, glm.fit ,K=10) $delta [1]
        }
        print("MSE cross-validation")
        print(mean(cv.error.10))
      }
    }
  }
  return (data_model_selection)
}
new_data=backwardElim(final_political_data,25,kfold=FALSE)
```

###Step 2: Variable Analysis

The list of significant variables listed. Variables that can be included are modified into more descriptive level names.

```{r}
political_data=subset(political_data, select=c(Left_Right_Wing, Gender, Education, Union_Membership, Union_Membership_Family, Employ_Status, Occupation, Public_Private_Employ, Employ_Status_Spouse, Household_Income, Number_Household, Religiousity, Birth_COuntry, Public_Expense_Health, Public_Expense_Edu, Public_Expense_Defense, Public_Expense_Pension, Public_Expense_Police, Public_Expense_Welfare, Improv_Standard, Economy, Gov_Action_Dif_Income, Satisfaction_Democrat))

final_political_data=na.omit(political_data)
```

```{r}
dim(final_political_data)
any(is.na(final_political_data))
```

```{r, results="hide"}
final_political_data$Female=ifelse(final_political_data$Gender==1,0,1)
final_political_data$Gender=NULL

any(is.na(final_political_data))

final_political_data <- with(final_political_data,
                           mutate(final_political_data,
                                  Education=case_when(
                                Education==1 ~ "Early Childhood Education",
                                Education==2 ~ "Primary School",
                                Education==3 ~ "Lower Secondary", 
                                Education==4 ~ "Upper Secondary", 
                                Education==5 ~ "Post-Secondary Non-Tertiary", 
                                Education==6 ~ "Short-cycle Tertiary", 
                                Education==7 ~ "Bachelor or Equivalent", 
                                Education==8 ~ "Master or Equivalent", 
                                Education==9 ~ "Doctoral or Equivalent", 
                                Education==96 ~ "No Education",
                                is.na(Education) ~ "Missing")))
any(is.na(final_political_data))


final_political_data <- with(final_political_data,
  mutate(final_political_data,
         Union_Membership=case_when(
           Union_Membership==1 ~ 1,
           Union_Membership==2 ~ 0)))

any(is.na(final_political_data))


final_political_data <- with(final_political_data,
  mutate(final_political_data,
         Union_Membership_Family=case_when(
           Union_Membership_Family==1 ~ "1",
           Union_Membership_Family==2 ~ "0"
           ,
           is.na(Union_Membership_Family) ~ "Missing")))

any(is.na(final_political_data))


final_political_data <- with(final_political_data,
  mutate(final_political_data,
         Employ_Status=case_when(
           Employ_Status==1 ~ "Full-time",
           Employ_Status==2 ~ "Part-time",
           Employ_Status==3 ~ "Less than 15 hours",
           Employ_Status==4 ~ "Help Family",
           Employ_Status==5 ~ "Unemployed",
           Employ_Status==6 ~ "Student",
           Employ_Status==7 ~ "Retired",
           Employ_Status==8 ~ "Housewife",
           Employ_Status==9 ~ "Disabled",
           Employ_Status==10 | Employ_Status ==11 | Employ_Status==12 ~ "Other",
           is.na(Employ_Status) ~"Missing")))

any(is.na(final_political_data))


final_political_data <- with(final_political_data,
  mutate(final_political_data,
         Gov_Action_Dif_Income=case_when(
          Gov_Action_Dif_Income==1 ~ "Strongly Agree",
          Gov_Action_Dif_Income==2 ~ "Somewhat Agree",
          Gov_Action_Dif_Income==3 ~ "Neither",
          Gov_Action_Dif_Income==4 ~ "Somewhat Disagree",
          Gov_Action_Dif_Income==5 ~ "Strongly Disagree",
           is.na( Gov_Action_Dif_Income) ~"Missing")))
any(is.na(final_political_data))


final_political_data <- with(final_political_data,
  mutate(final_political_data,
         Employ_Status_Spouse=case_when(
           Employ_Status_Spouse==1 ~ "Full-time",
           Employ_Status_Spouse==2 ~ "Part-time",
           Employ_Status_Spouse==3 ~ "Less than 15 hours",
           Employ_Status_Spouse==4 ~ "Help Family",
           Employ_Status_Spouse==5 ~ "Unemployed",
           Employ_Status_Spouse==6 ~ "Student",
           Employ_Status_Spouse==7 ~ "Retired",
           Employ_Status_Spouse==8 ~ "Housewife",
           Employ_Status_Spouse==9 ~ "Disabled",
           Employ_Status_Spouse==10 | Employ_Status_Spouse==11 | Employ_Status_Spouse==12~ "Other",
           is.na(Employ_Status_Spouse) ~"Missing")))
any(is.na(final_political_data))


final_political_data = final_political_data %>%
  mutate(Occupation=as.numeric(as.character(Occupation)))

final_political_data <- with(final_political_data,
                           mutate(final_political_data,
                                  Occupation=case_when(
                                  Occupation <100 ~ "Arm Forces",
                                  Occupation >=100 & Occupation < 200 ~ "Managers",
                                  Occupation >=200 & Occupation < 300 ~ "Professionals",
                                  Occupation >=300 & Occupation < 400 ~ "Technicians",
                                  Occupation >=400 & Occupation < 500 ~ "Clerical Support",
                                  Occupation >=500 & Occupation < 600 ~ "Service & Sales",
                                  Occupation >=600 & Occupation < 700 ~ "Agricultural, Forestry, and Fishery",
                                  Occupation >=700 & Occupation < 800 ~ "Craft and Trade",
                                  Occupation >=800 & Occupation < 900 ~ "Plant and Machine Operators",
                                  Occupation >=900 & Occupation <= 962 ~ "Elementary Occupation",
                                  is.na(Occupation) ~ "Wrong Value")))

any(is.na(final_political_data))


final_political_data <- with(final_political_data,
                           mutate(final_political_data, 
                                  Public_Private_Employ=case_when(
                             Public_Private_Employ==1 ~ "Public",
                             Public_Private_Employ==2 ~ "Private", 
                             Public_Private_Employ==3 ~ "Mixed",
                             Public_Private_Employ==4 ~ "Third Sector/NPO", 
                             Public_Private_Employ==5 | Public_Private_Employ == 6 ~ "Other/Self-Employed",
                             is.na(Public_Private_Employ) ~ "Missing")))

final_political_data <- with(final_political_data,
                           mutate(final_political_data, 
                                  Household_Income=case_when(
                             Household_Income==1 ~ "Lowest Quantile",
                             Household_Income==2 ~ "Second Lowest Quantile", 
                             Household_Income==3 ~ "Third Lowest Quantile",
                             Household_Income==4 ~ "Fourth Lowest Quantile", 
                             Household_Income==5 ~ "Highest Quantile",
                             is.na(Household_Income) ~ "Missing")))

final_political_data <- with(final_political_data,
                           mutate(final_political_data, 
                                  Religiousity=case_when(
                             Religiousity==1 ~ "Not Religious",
                             Religiousity==2 ~ "Not Very Religious", 
                             Religiousity==3 ~ "Somewhat Religious",
                             Religiousity==4 ~ "Very Religious", 
                             is.na(Religiousity) ~ "Missing")))

final_political_data <- with(final_political_data,
                           mutate(final_political_data, 
                                  Public_Expense_Health=case_when(
                             Public_Expense_Health==1 ~ "Much more than now",
                             Public_Expense_Health==2 ~ "Somewhat more than now", 
                             Public_Expense_Health==3 ~ "The same as now",
                             Public_Expense_Health==4 ~ "Somewhat less than now", 
                             Public_Expense_Health==5 ~ "Much less than now",
                             is.na(Public_Expense_Health) ~ "Missing")))

final_political_data <- with(final_political_data,
                           mutate(final_political_data, 
                                  Public_Expense_Edu=case_when(
                             Public_Expense_Edu==1 ~ "Much more than now",
                             Public_Expense_Edu==2 ~ "Somewhat more than now", 
                             Public_Expense_Edu==3 ~ "The same as now",
                             Public_Expense_Edu==4 ~ "Somewhat less than now", 
                             Public_Expense_Edu==5 ~ "Much less than now",
                             is.na(Public_Expense_Edu) ~ "Missing")))

final_political_data <- with(final_political_data,
                           mutate(final_political_data, 
                                  Public_Expense_Defense=case_when(
                             Public_Expense_Defense==1 ~ "Much more than now",
                             Public_Expense_Defense==2 ~ "Somewhat more than now", 
                             Public_Expense_Defense==3 ~ "The same as now",
                             Public_Expense_Defense==4 ~ "Somewhat less than now", 
                             Public_Expense_Defense==5 ~ "Much less than now",
                             is.na(Public_Expense_Defense) ~ "Missing")))

final_political_data <- with(final_political_data,
                           mutate(final_political_data, 
                                  Public_Expense_Pension=case_when(
                             Public_Expense_Pension==1 ~ "Much more than now",
                             Public_Expense_Pension==2 ~ "Somewhat more than now", 
                             Public_Expense_Pension==3 ~ "The same as now",
                             Public_Expense_Pension==4 ~ "Somewhat less than now", 
                             Public_Expense_Pension==5 ~ "Much less than now",
                             is.na(Public_Expense_Pension) ~ "Missing")))

final_political_data <- with(final_political_data,
                           mutate(final_political_data, 
                                  Public_Expense_Police=case_when(
                             Public_Expense_Police==1 ~ "Much more than now",
                             Public_Expense_Police==2 ~ "Somewhat more than now", 
                             Public_Expense_Police==3 ~ "The same as now",
                             Public_Expense_Police==4 ~ "Somewhat less than now", 
                             Public_Expense_Police==5 ~ "Much less than now",
                             is.na(Public_Expense_Police) ~ "Missing")))

final_political_data <- with(final_political_data,
                           mutate(final_political_data, 
                                  Public_Expense_Welfare=case_when(
                             Public_Expense_Welfare==1 ~ "Much more than now",
                             Public_Expense_Welfare==2 ~ "Somewhat more than now", 
                             Public_Expense_Welfare==3 ~ "The same as now",
                             Public_Expense_Welfare==4 ~ "Somewhat less than now", 
                             Public_Expense_Welfare==5 ~ "Much less than now",
                             is.na(Public_Expense_Welfare) ~ "Missing")))

final_political_data <- with(final_political_data,
                           mutate(final_political_data, 
                                  Improv_Standard=case_when(
                             Improv_Standard==1 ~ "Very likely",
                             Improv_Standard==2 ~ "Somewhat likely", 
                             Improv_Standard==4 ~ "Somewhat unlikely", 
                             Improv_Standard==5 ~ "Very unlikely",
                             is.na(Improv_Standard) ~ "Missing")))

final_political_data <- with(final_political_data,
                           mutate(final_political_data, 
                                  Economy=case_when(
                             Economy==1 ~ "Better",
                             Economy==3 ~ "Same",
                             Economy==5 ~ "Worse",
                             is.na(Economy) ~ "Missing")))

final_political_data <- with(final_political_data,
                           mutate(final_political_data, 
                            Satisfaction_Democrat=case_when(
                             Satisfaction_Democrat==1 ~ "Very Satisfied",
                             Satisfaction_Democrat==2 ~ "Fairly Satisfied",
                             Satisfaction_Democrat==4 ~ "Not very satisfied",
                             Satisfaction_Democrat==5 ~ "Not at all satisfied",

                             is.na(Satisfaction_Democrat) ~ "Missing")))

```

Convert character variables to factor

```{r}
final_political_data=final_political_data %>%
  mutate_if(is.character,as.factor)
```

Make the bar charts: 
```{r}
barChart <- function(data, variable, x_label, title, color){
  myplot <- ggplot(data, aes(x = variable), 
                        y = count)
  myplot + geom_bar(aes(), fill=color) +
  labs(y="Number of people", x=x_label)+
    ggtitle(title) +
    theme(axis.text.x = element_text(angle = 60, hjust = 1))

}
```

```{r, results="hide"}
barChart(final_political_data, final_political_data$Left_Right_Wing, "Political Spectrum", "Political Spectrum distribution", "purple")

barChart(final_political_data, final_political_data$Education, "Education Level", "Education Level Distribution", "darkslateblue")

barChart(final_political_data, final_political_data$Public_Private_Employ, "Employment Sector", "Employment Sector Distribution", "coral3")

barChart(final_political_data, final_political_data$Occupation, "Occupation", "Occupation Distribution", "aquamarine4")

barChart(final_political_data, final_political_data$Household_Income, "Household Income", "Household Income  Distribution", "forestgreen")

barChart(final_political_data, final_political_data$Household_Income, "Household Income", "Household Income  Distribution", "forestgreen")

barChart(final_political_data, final_political_data$Religiousity, "Religiousity", "Religiousity Distribution", "cornflowerblue")

barChart(final_political_data, final_political_data$Satisfaction_Democrat, "Satisfaction of Democracy", "Satisfaction of Democracy", "darkseagreen4")

barChart(final_political_data, as.factor(final_political_data$Female), "Gender: 0 is male, 1 is female", "Distribution of Female", "pink3")

barChart(final_political_data, final_political_data$Birth_COuntry, "Country", "Distribution of Country", "skyblue3")



```

```{r}
#Create a new table of public expenditure opinion
expenditure_opinion=data.frame(cbind(as.character(final_political_data$Public_Expense_Health),
                                     as.character(final_political_data$Public_Expense_Edu),
                                     as.character(final_political_data$Public_Expense_Defense), 
                                     as.character(final_political_data$Public_Expense_Police),
                                     as.character(final_political_data$Public_Expense_Welfare)))

names(expenditure_opinion)=c("Health","Education","Defense", "Police", "Welfare")

#Reshaping the table 
expenditure_opinion <- expenditure_opinion %>%
  gather(key="Expense", value="Opinion")

#Plot it 
myplot <- ggplot(expenditure_opinion, aes(fill=Expense, x = Opinion), 
                        y = count)
  myplot + geom_bar(aes(), position="dodge")+
  labs(y="Number of people", x="Opinion on public expenditure")+
    ggtitle("Opinion on public expenditure") +
    theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

Set the countries with few observations as "Other":
```{r, results="hide"}
rareLevelAsOther <- function (variable, var_name, mydata, limit){
  freq_table=as.data.frame(tally(~variable, data=mydata))
  variable=as.factor(ifelse(freq_table[match(variable, freq_table[,1]),2]>limit, as.character(variable), "Other"))
  index=getIndexFromName(mydata,var_name)
  mydata[,index]=variable
  return(mydata)
}

final_political_data=rareLevelAsOther(final_political_data$Birth_COuntry, "Birth_COuntry", final_political_data, 50)

tally(~final_political_data$Birth_COuntry)
```

Check for multicollinearity: 
```{r, result="hide"}
reg_all=lm(Left_Right_Wing~.,data=final_political_data)
vif(reg_all)
```

Now I run the backward selection algorithm again and pick the model with high R-squared and low AIC
```{r}
new_data=backwardElim(final_political_data,15,kfold=TRUE)
```

The second model is the best one. I choose the second model.

Reset the levels of factor variables 
```{r}
final_political_data$Household_Income <- relevel(final_political_data$Household_Income, ref="Lowest Quantile")
final_political_data$Religiousity <- relevel(final_political_data$Religiousity, ref="Not Religious")
final_political_data$Education <- relevel(final_political_data$Education, ref="Early Childhood Education")
final_political_data$Occupation <- relevel(final_political_data$Occupation, ref="Elementary Occupation")
final_political_data$Employ_Status <- relevel(final_political_data$Employ_Status, ref="Full-time")
final_political_data$Public_Private_Employ <- relevel(final_political_data$Public_Private_Employ, ref="Public")
final_political_data$Employ_Status_Spouse <- relevel(final_political_data$Employ_Status_Spouse, ref="Unemployed")
final_political_data$Public_Expense_Health <- relevel(final_political_data$Public_Expense_Health, ref="The same as now")
final_political_data$Birth_COuntry <- relevel(final_political_data$Birth_COuntry, ref="Other")

final_political_data$Public_Expense_Defense <- relevel(final_political_data$Public_Expense_Defense, ref="The same as now")
final_political_data$Public_Expense_Welfare <- relevel(final_political_data$Public_Expense_Welfare, ref="The same as now")
final_political_data$Public_Expense_Police <- relevel(final_political_data$Public_Expense_Police, ref="The same as now")
final_political_data$Public_Expense_Edu <- relevel(final_political_data$Public_Expense_Edu, ref="The same as now")
final_political_data$Improv_Standard <- relevel(final_political_data$Improv_Standard, ref="Very unlikely")
final_political_data$Economy <- relevel(final_political_data$Economy, ref="Same")
final_political_data$Satisfaction_Democrat <- relevel(final_political_data$Satisfaction_Democrat, ref="Very Satisfied")

```

#Model and Result

Regression Model: 
```{r}
reg=lm(Left_Right_Wing ~ Education + Union_Membership + Union_Membership_Family + Employ_Status + Occupation + Public_Private_Employ+ Employ_Status_Spouse + Household_Income + Religiousity + Birth_COuntry + Public_Expense_Welfare+ Public_Expense_Police + Public_Expense_Health + Public_Expense_Defense + Public_Expense_Edu + Improv_Standard + Economy + Gov_Action_Dif_Income  + Satisfaction_Democrat, data=final_political_data)
```

Result 
```{r, results="hide"}
sum_reg=summary(reg)
sum_reg$coefficients
#write.csv(sum_reg$coefficients, "results.csv")
```

```{r}
anova(reg)
```

Test for Equality of Variance Assumption
```{r}
ncvTest(reg)
```

Test for Normality Assumption
```{r}
plot(reg,which=c(2))
```

